\documentclass{article}

\usepackage[a4paper,total={6in, 10in}]{geometry}
\usepackage{xcolor}
\usepackage[fontsize=14pt]{fontsize}

\begin{document}

\title{Research Proposal}
\author{Jonathan Reicher \\ Shachar Itzhaki}
\maketitle

\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
\setlength{\parskip}{0.1cm}

\section*{Problem Statement}
In the intersection between the worlds of mathematical theory, formal logic,
and programming, exists a species of tools called proof assistants.
These are programming languages, meant not for building software, but for
building mathematical proofs.
Proof assistants, contrary to pen and paper, check formalized proofs for
correctness and soundness.
These systems have existed for many years, but recently, one in particular has
been gaining traction.

Lean (\todo{cite?}) is an interactive proof assistant geared for a general math
audience.
Two things that make it especially appealing are its large ecosystem and its
intuitive syntax.
Despite that, there are some challenging aspects of adopting Lean, and one in
particular is how complex its semantics and type system are, and how.

We propose building a system that will reduce the friction of using Lean by
being more ``forgiving'' and less formal. The system will allow users to write
down proofs in way that humans can read and understand as written, with parts of
the proof being translated to Lean, to help a user start formalizing their
proof in Lean.
This workflow is in accordance to how researchers tend to use Lean, as a formal
proof in Lean often comes as a supplementary part of a paper proof inside a
research paper.

\section*{Existing Solutions}
For starting a project in Lean, one can reach for any off-the-shelf
generative large language model such as ChatGPT.
These systems have gotten good at generating good and correct Lean code.
One can write their paper, give it to the system, and prompt it to generate a
formal Lean proof.
There are even tools in place to help large language models work with Lean such
Aristotle.
These systems suffer a number of drawbacks: They lack reproducibility, are
usually based on cloud services, and are not fit with an interactive and
iterative workflow.

There are also a number of automated proof assistants that can be embedded into
Lean, such as Aesop and Grind. These systems work on top of Lean by
generating parts of a proof that you request.
This is useful as part of interactive theorem proving, but they do not produce a
readable proof.
They can work off of a paper, but that requires manual work.

\todo{Mention open ai’s paper that adi sent}

\section*{Preliminary Work}
We started from taking a look at a case study example of a proof in Lean.

Can you cover a $10 \times 10$ board with $2 \times 1$ tiles, such that the
number of horizontal and vertical tiles is the same?

This file explains Filmus's solution and proof to the puzzle, "pen and paper"
style. Spoiler: _You can't!_

Started from Yuval’s domino example. Tried to encode the domain and the solution
in LEAN.
embed proof.md and a matching lean code that we expect

\section*{References}

\end{document}
